\begin{thebibliography}{99}
\bibitem{bib01} Web page of Baytulhabeeb, an artist, \url{https://bit.ly/islamic_cal_history}, accessed on Sep 4, 2020.
\bibitem{bib02} Arabetics™, a private foundry and consulting firm, specializing in Arabic type and lettering designs, “Roots of Modern Arabic Script:  From Musnad to Jazm”, \url{https://bit.ly/islamic_cal_history_2}, accessed on Sep 4, 2020.
\bibitem{bib03} “Islamic Calligraphy”, \url{https://bit.ly/Islamic_cal_wiki}, accessed on Sep 4, 2020.
\bibitem{bib04} By Julia Kaestle , “Arabic calligraphy as a typographic exercise”, \url{https://bit.ly/cal_styles}, accessed on Sep 4, 2020.
\bibitem{bib05} Haji Noor Den, Portfolio, \url{http://www.hajinoordeen.com/about.html}, accessed on Sep 4, 2020.
\bibitem{bib06} Mohammad Zakrya, Portfolio, \url{https://mohamedzakariya.com}, accessed on Sep 4, 2020.
\bibitem{bib07} Kamel Al Baba, Mokhtar Al Baba, Portfolio, \url{http://www.arabiccalligraphy.com}, accessed on Sep 4, 2020.
\bibitem{bib08} Abed Yaman, “A look at the history of Arabic calligraphy” \url{https://bit.ly/islamic_cal_stages}, accessed on Sep 4, 2020.
\bibitem{bib09} M. A.-de Lemos, and E. V. Liberado, “Industrial robotics applied to education”, Proceedings of 2011 International Conference on Computer Science and Network Technology.
\bibitem{bib10} Robotics in Agriculture: Types and Applications, \url{https://bit.ly/ind_robots_in_agri}, accessed on Sep 4, 2020.
\bibitem{bib11} A robot playing table tennis, \url{https://www.kuka.com/timo}, accessed on Sep 4, 2020.
\bibitem{bib12} A printing robot, \url{https://bit.ly/ind_robot_cal}, accessed on Sep 4, 2020.
\bibitem{bib13} M. Bilal, A. Raza, M. Rizwan, M. Ahsan, H. F. Maqbool, S. Abbas Zilqurnain Naqvi, “Towards Rehabilitation of Mughal Era Historical Places using 7 DOF Robotic Manipulator”, in Proceedings, IEEE International Conference on Robotics and Automation in Industry, pp. 1-6, 2019.
\bibitem{bib14} GIMP, GNU Image Manipulation Program Developers Resources, \url{https://bit.ly/gimp_developers}, accessed on July 7, 2021.
\bibitem{bib15} Inkscape Extensions, \url{https://bit.ly/inkscape_developers}, accessed on July 7, 2021.
\bibitem{bib16} Wacom Intuos, \url{https://bit.ly/wacom_intuos_official}, accessed on July 7, 2021.
\bibitem{bib17} Lenovo Thinkpad x380, \url{https://bit.ly/lenovo_thinkpad_x380}, accessed on July 7, 2021.
\bibitem{bib18} Microsoft Surface Pro 7, \url{https://bit.ly/ms_surface_pro_7}|, accessed on July 7, 2021.
\bibitem{bib19} George R. R. Martin, \emph{``A Game of Thrones''}, Chapter $30$.
\bibitem{bib20} Project code repository on GitHub, \url{https://github.com/umartechboy/Thesis_2017-MS-MC-17}|, accessed on August 8, 2021.
    \end{thebibliography} 