\section{Introduction}
{
    Islamic calligraphy is an art having a history that dates back to the seventh century \cite{bib01, bib02}. It has witnessed many evolutionary stages \cite{bib02, bib03} and has been used by artists speaking several different languages \cite{bib04} and sharing uncommon biographies \cite{bib05,bib06,bib07,bib08}. Unfortunately though, the industrial age and the advent of technology has not spared this beautiful art when it claims to provide better alternatives for almost everything related to human beings. Discovery of new facets of calligraphy aside, with the prevalence of modern technologies and resulting lack of expertise in this domain, the very existence of Islamic calligraphy now faces a serious threat. Public buildings and infrastructure that once used to be a showcase for the most laudable artists of the time have turned in-to museums; awaiting to be wiped away slowly with each round of the monsoon and every splash of the ocean’s waves.

    Potentially, we can use robotic dexterity to help us in this domain. Industrial robots have already been used outside the industry to do unorthodox tasks \cite{bib09, bib10,bib11,bib12} and they can surely uplift this art as well. At the very least, they can be employed in restoration and replication of existing calligraphy work \cite{bib13}. In other words, they can be used as printers, or rather one may say, “painters” that give an extra hand to the calligraphy artists to open up a new dimension of the art that can not only revamp the existing calligraphy sites but also create new art.
    Mechanized/robotic drawing of the Islamic calligraphy scripts requires not just the ink-mark information but also the information about the tool movement \cite{bib03}. Specially, using a flexible flat head brush instead of a solid round tip pen and all that to draw on un-even surfaces, makes the job extremely special indeed. A robot needs to take special care about the orientation and downwards force of the tool as well.

    In a nutshell, the main problem can be divided in two major sections. First, transforming the printed scripts into machine data and second, recreating the scripts using a robotic end effector.
    To solve the first part, instead of doing image processing, we propose a new way of transforming the existing scripts into machine data; the “Rotation/twisting Bezier Spline”. The idea is to bring real artists in the process. For the new scheme to be fully tested, we wrote a fully featured graphical spline editor and analyzer called “Gregor”. The tool was tested and tuned with the help of multiple real-world calligraphers.

    Then we test the trace effectivity of the so-called rotating/twisting splines by taking specimens written in two Qat’s. We use image processing to quantitatively compare the source to the traced script.
    In parallel, we developed a simulator of a six degrees of freedom robot, called “Drogon”. The simulator boasts a 3D view finder, lets us change the physical parameters of the robot, provides some useful tools to analyze, test and tune different aspects of the simulator itself, and last but not the least, tools to input scripts developed with twisting Bezier splines in to the simulated world and then quantitatively test how the robot performs given the target.

    Last but not the least part of this project is an effort to efficiently document each aspect; the code, software architecture, the software tools, the physics behind the simulator and the areas which one can carry over for further research and improvement. Since not all of such information can be printed, we have set up a public Github repository where one can not only fetch information but also contribute easily to the project.
